---
title: "City Health Service impact on Public Health"
author: "Deepti Vijay Khandagale"
author: "Satwika Reddy Kondi"
date: '08/05/2022 '
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd(getwd())
```

## R Markdown
```{r}
rm(list=ls())
library("dplyr")
library("tidyverse")
library("skimr")
library("ggplot2")
```
Health is the most important aspect of life. In today's world, with unhealthy food habits and lifestyle foods, the chance of weight gain, heart diseases and Blood Pressure  related problems are increasing. On the other hand, medical treatments have become expensive. As said, `Prevention is better than cure`, the health services around the United States have taken up a project to focus on public health and prevent the risk of disease and health issues. One of the interesting projects is `PLACES` which works on the analysis of risks and diseases and habits common across the population.

# BACKGROUND
##Briefly explain what problem you’re trying to solve through data analysis.
`PLACES` the expansion of The 500 Cities Project, is a partnership project between the Center for Disease Control (CDC) and the Robert Wood Johnson. It focuses on providing towards model-based analysis of health estimates for local areas across the United States. For the first time, it supplied data for cities and census tracts, many of which covered multiple counties across the United States. These data can be filtered (by city and/or tracts, as well as by measure) and downloaded by end-users for use in different analyses.
This initiative provided the display, retrieval and exploration of health care data, risk factors and habits that have a significant impact on the health of the population.

## Who can benefit from your data analysis (i.e., who are stakeholders)? Specify detailed justifications on why your analysis will be beneficial to particular groups of people, researchers, or organizations.

* The analysis  enabled local health departments and authorities to better understand the burden and geographic distribution of health measures in their areas, independent of population size or rurality, and to aid them in planning public health actions.
This project employed small area estimating methods to acquire 27 chronic illness indices for the 500 largest American cities by reporting city and census tract-level data. The data were made public through the "500 Cities" website, which allowed visitors to browse, examine, and download data at the city and tract levels. Despite the limitation of data till
county levels, this approach supplemented current surveillance data, allowing researchers to gain a better understanding of the health challenges that people of that city or census tract face.

**PART TWO**
# Nature of the Data Curation
## Who (company, agency, organization) collected the data?
* The only data used will be the CDC's 2018 500 Cities Data. The center for Disease Control is open about its data and techniques, as well as the limitations and issues, and their data is in the public domain (such as self-reported data).

## Who they are, what do they do?
* The Centers for Disease Control and Prevention (CDC) works around the clock to protect America from both foreign and domestic health, safety, and security threats. CDC helps communities and citizens confront disease, whether it originates at home or abroad, is chronic or acute, curable or avoidable, caused by human error or a premeditated attack.
* The Centers for Disease Control and Prevention (CDC) works to strengthen the health security of our country. As the nation's health protection agency, the CDC saves lives and protects individuals from health threats. The Centers for Disease Control and Prevention (CDC) conducts critical research and disseminates health information to protect the United States from costly and hazardous health problems, as well as responding to them when they arise.

## Why did they collect the data (purpose)?  
* The PLACES Project took over from the 500 Cities Project in December 2020. It was a collaboration between the Centers for Disease Control and Prevention, the Robert Wood Johnson Foundation, and the CDC Foundation. It offered small area estimates for chronic disease risk factors, health outcomes, and clinical preventive care utilization for the major 500 cities in the United States at the city and census tract level. These small-area estimates aided cities and local health departments in better understanding the burden and spatial distribution of health-related factors in their jurisdictions, allowing them to better plan public health interventions.
* Individual cities and groupings of cities, as well as other stakeholders, might have used this high-quality, small-area epidemiologic data to assist create and implement effective and focused prevention programs, identify developing health problems, and establish and monitor critical health targets. 
* City planners and elected officials, for example, may have wished to utilize this information to target neighborhoods with high rates of smoking or other health-risk behaviors for successful interventions.
*The good thing about the dataset is that it is organized in a dataframe hence making it easier for analysis. However, the dataset is not clean i.e there are unnecessary and null values in the data set that needs to be cleaned. Hence, we will do a data cleaning for accurate analysis and predictions. The dataset is available in the public domain making it easier for researchers and analysts to use it and make recommendations to the relevant stakeholders.

## What is the nature of the data given the purpose of the data collection (e.g., any bias)?Usually, many datasets are NOT collected for data scientists themselves, but as a byproduct of organizational process. Because of this reason, it is important to understand the nature of the data. 


# Given the nature of the data, how can you adjust and leverage the data (i.e., what are pros and cons of the data and how can you overcome it)?
Pros
*The data set is organised in a dataframe hence making it easier for analysis
Cons

*There are missing values that could affect the results.This is overcomes by removing them from the datset.
*There are unnecessary variables and they will be removed from the dataset.

# Is there any privacy, quality, or other issues with this data?

* The dataset is availble in the public domain making it easier for researchers to analyse and make recommedations to the relevant stakeholders.



**PART 3 QUESTIONS**
## Does the city make a difference in how much a population uses preventative services?
* The variables within the study that a city can directly influence are likely the use of preventative services and healthy behaviors, which may then impact the health outcomes. To test that hypothesis, we'll begin by looking at preventative services which consists of a number of outcomes.

## Does the city influence the impact on healthy behaviours?
The cities could take measures that could significantly influence positivly on the healthy behaviours within the popupation. Some of the variales that will help answer this question include:\\
*"No leisure-time physical activity among adults aged >=18 Years" (LPA)
*"Sleeping less than 7 hours among adults aged >=18 Years" (SLEEP)
*"Binge drinking among adults aged >=18 Years" (BINGE)
*"Current smoking among adults aged >=18 Years" (CSMOKING)
## What can the city do to drive greater use of the services?
This refers to the measures that the cities would undertake to increase the utilization of services such as insurance.


**PART 3 Requirements and Resources needed**
## What software and hardware resources you have used in this project?
Rstudio was used to analyse the dataset.
the necesary libraries include:
ggplot2 for visualization
tidyverse for cleaning the dataset
dplyr for data manipulation
Tool: Rmarkdown
## What kinds of pre-processes were needed to make use of the data, and why?
* Removal of variables that are not necessary for analysis
* Removal of duplicates.
* Removal of extreme values

**PART 4 Descriptive Analysis**

## Briefly describe the dataset

#Loading the dataset
```{r}
data_health<-read.csv("500_Cities__Local_Data_for_Better_Health__2019_release.csv",header=T)#loading the dataset
head(data_health)
str(data_health)
dim(data_health)
summary(data_health)
```




```{r}
colnames(data_health)
skim_without_charts(data_health)

# For visualizing missing values
# data_health %>% summarise_all(list(~is.na(.))) %>% pivot_longer(everything(), names_to = "variables", values_to = "missing" ) %>% count(variables, missing) %>% ggplot(aes(y=variables, x=n, fill=missing)) + geom_col()+ scale_fill_manual(values=c("skyblue","red"))+ theme(axis.title.y=element_blank())

```

#Data Cleaning & Transformation
```{r cars}
#Removing unncessary variables
data <- select(data_health, -"StateDesc",-"DataSource", -"Data_Value_Unit", -"DataValueTypeID", -"UniqueID", 
                      -"Measure", -"GeoLocation", -"Short_Question_Text", -"Low_Confidence_Limit",-"High_Confidence_Limit", -"Data_Value_Footnote_Symbol", -"Data_Value_Footnote", -"Category", -"CategoryID", -"CityFIPS", -"Year")
data <- select(data_health,-"StateDesc",-"DataSource", -"Data_Value_Unit", -"DataValueTypeID", -"UniqueID", 
                      -"Measure", -"GeoLocation", -"Short_Question_Text", -"Low_Confidence_Limit",-"High_Confidence_Limit", -"Data_Value_Footnote_Symbol", -"Data_Value_Footnote", -"Category", -"CategoryID", -"CityFIPS", -"Year")
head(data)
str(data)
```

```{r pressure, echo=FALSE}
#Renaming to lowercase with underscores for style guide purposes. 
data <- rename(data, geographic_level = GeographicLevel, state_abbr = StateAbbr, data_value_type = Data_Value_Type, tract_fips = TractFIPS, city_name = CityName,  measure_id = MeasureId, data_value = Data_Value, population_count = PopulationCount)

colnames(data)
```

## Prepare and describe relevant metadata (types of attributes/variables in the dataset)

```{r}
str(data)
glimpse(data)
```

##  Provide some descriptive statistics so readers can understand the data without actually looking into it (e.g., mean, SD, frequency, distribution, network structure, etc.)

```{r}

#converting to numeric 
data$population_count<-as.numeric(data$population_count)
#lst the column names
colnames(data)
skim_without_charts(data)
#summary statistics
summary(data)
```










```{r}
library(tidyr)
cities <- data %>%
  filter(geographic_level == "City", state_abbr != "US", data_value_type == "Crude prevalence") %>%
  select(-tract_fips) %>%
  arrange(city_name) %>%
  pivot_wider(names_from = measure_id, values_from = data_value) %>%
  tidyr::unnest(cols = c(STROKE, HIGHCHOL, BPHIGH, BPMED, CHOLSCREEN, OBESITY, PHLTH, 
                         DENTAL, CSMOKING, DIABETES, LPA, CANCER, PAPTEST, KIDNEY, 
                         ARTHRITIS, ACCESS2, COREW, COPD, COREM, SLEEP, CHECKUP, BINGE, 
                         CHD, MHLTH, COLON_SCREEN, TEETHLOST, CASTHMA, MAMMOUSE))

head(cities)
```

```{r}
census <- data %>%
  filter(geographic_level != "City", state_abbr != "US") %>%
  arrange(city_name) %>%
  pivot_wider(names_from = measure_id, values_from = data_value) %>%
  tidyr::unnest(cols = c(STROKE, HIGHCHOL, BPHIGH, BPMED, CHOLSCREEN, OBESITY, PHLTH, 
                         DENTAL, CSMOKING, DIABETES, LPA, CANCER, PAPTEST, KIDNEY, 
                         ARTHRITIS, ACCESS2, COREW, COPD, COREM, SLEEP, CHECKUP, BINGE, 
                         CHD, MHLTH, COLON_SCREEN, TEETHLOST, CASTHMA, MAMMOUSE))

head(census)
skim_without_charts(census)
```
```{r}
#Removing Paptest
colnames(cities)
census <- census %>%
  select(-"PAPTEST")
cities <- cities %>%
  select(-PAPTEST)

# Renaming the revised tables for style guide purposes: 
cities <- rename(cities, stroke = STROKE, highchol = HIGHCHOL, bphigh = BPHIGH, bpmed = BPMED, 
                       cholscreen = CHOLSCREEN, obesity = OBESITY, phlth = PHLTH, dental = DENTAL, 
                       csmoking = CSMOKING, diabetes = DIABETES, lpa = LPA, cancer = CANCER,
                       kidney = KIDNEY, arthritis = ARTHRITIS, access2 = ACCESS2, corew = COREW, 
                       corem = COREM, copd = COPD, sleep = SLEEP, checkup = CHECKUP, binge = BINGE,
                       chd = CHD, mhlth = MHLTH, colon_screen = COLON_SCREEN, teethlost = TEETHLOST, 
                       casthma = CASTHMA, mammouse = MAMMOUSE)



census <- rename(census, stroke = STROKE, highchol = HIGHCHOL, bphigh = BPHIGH, 
                             bpmed = BPMED, cholscreen = CHOLSCREEN, obesity = OBESITY, phlth = PHLTH, 
                             dental = DENTAL, csmoking = CSMOKING, diabetes = DIABETES, lpa = LPA, 
                             cancer = CANCER, kidney = KIDNEY, arthritis = ARTHRITIS, access2 = ACCESS2, 
                             corew = COREW, corem = COREM, copd = COPD, sleep = SLEEP, checkup = CHECKUP, 
                             binge = BINGE, chd = CHD, mhlth = MHLTH, colon_screen = COLON_SCREEN, 
                             teethlost = TEETHLOST, casthma = CASTHMA, mammouse = MAMMOUSE)



```
#Bias

```{r}
str(census)
census$population_count= as.numeric(census$population_count)
census<<-na.omit(census)
states <- census %>% 
  group_by(state_abbr) %>%
  filter(geographic_level != 'City', state_abbr != "US") %>%
  summarize("population" = sum(population_count), "cities" = length(unique(city_name))) %>%
  arrange(-cities)

states$population= as.numeric(states$population)
print(states)

ggplot(states, aes(x=reorder(state_abbr,population), y=population )) + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 90)) + scale_x_discrete("US States")


```
This data is skewed considerably in favor of a few states. For a variety of reasons, including culture, legislation, and weather, we can't assume that what works in California would work in Alaska. However, 11 states had only one city investigated, while California has 83. The accuracy of my findings could therefore be affected by the client's location. This happened because the study concentrated on the country's largest cities, then added a few more to guarantee that every state was covered. With this in mind, it's understandable if you're concerned about how this would apply to a tiny town.


***RESEARCH QUESTIONS**

## Does the city make a difference in how much a population uses preventative services?
The usage of preventative services and healthy behaviors are likely the variables within the study that a city can directly influence, which may therefore impact health outcomes. To verify that theory, we'll start with preventative services, which include things like:
* "Current lack of health insurance among adults aged 18–64 Years," (ACCESS2)
* "Visits to doctor for routine checkup within the past Year among adults aged >=18 Years," (CHECKUP)
* Fecal occult blood test, sigmoidoscopy, or colonoscopy among adults aged 50–75 Years," (COLON_SCREEN)
* "Mammography use among women aged 50–74 Years," (MAMMOUSE)
* "Visits to dentist or dental clinic among adults aged >=18 Years," (DENTAL)
* "Cholesterol screening among adults aged >=18 Years," (CHOLSCREEN)
* "Older adult men aged >=65 Years who are up to date on a core set of clinical preventive services: Flu shot past Year, PPV shot ever, Colorectal cancer screening," (COREM)
* "Older adult women aged >=65 Years who are up to date on a core set of clinical preventive services: Flu shot past Year, PPV shot ever, Colorectal cancer screening," (COREW)
"Papanicolaou smear use among adult women aged 21–65 Years." (PAPTEST)


Is it true that the size of a city has an impact on how much a population uses preventative services? If there is a difference, it indicates that it is something that the city can influence and change. If not, it's possible that the United States as a whole has its own patterns of preventative service use, and the city will have to search elsewhere for effective ways to enhance its health.

```{r}
str(cities)
summary(select(cities, "access2", "checkup", "colon_screen", "cholscreen", "corem", "corew", "mammouse", "dental"))
```

```{r}
difference <- summarize(cities, "access2" = max(access2)-min(access2), "checkup" = max(checkup)-min(checkup), 
                        "colon_screen" = max(colon_screen)-min(colon_screen), "cholscreen" = max(cholscreen)-min(cholscreen), 
                        "corem" = max(corem)-min(corem), "corew" = max(corew)-min(corew), "mammouse" = max(mammouse)-min(mammouse), 
                        "dental" = max(dental)-min(dental))

difference <- pivot_longer(difference, everything(), names_to = "measure", values_to = "value")

ggplot(data = difference) +
  geom_col(mapping = aes(x = reorder(measure, -value), y = value), fill = 'blue') +
  labs(title = "Difference Between Cities", x = "Preventative Service", y = "Size of Difference")
```

```{r}
maxmin_preventative <- cities %>%
  filter(access2 == max(access2)|access2 == min(access2))

print(maxmin_preventative)
```
As you can see, there are variances between all of the preventative services, some of which are rather significant.
The gap between cities in terms of access2, a measure of how much of a population lacks health insurance, can be as large as 4.50 percent of the population vs. 44.40 percent.
Access2 has piqued my interest because it is the one that has the most difference between cities (albeit very narrowly), as well as for other reasons that will be detailed shortly. I'd like to learn more about its distribution:

```{r}
library(ggpubr)
plot_cities <-ggplot(data = cities) +
  geom_histogram(mapping = aes(x = access2), na.rm = TRUE, binwidth = 2) + 
  labs(title = "Distribution of Lack of Health Insurance", x = "Population Lacking Health Insurance", y = "Cities Lacking Health Insurance")

box_cities <- ggplot(data = cities) +
  geom_boxplot(mapping = aes(y = access2), na.rm = TRUE) + 
  labs(title = "Distribution of Lack of Health Insurance", y = "Population Lacking Health Insurance")

ggarrange(plot_cities, box_cities,  ncol = 2, nrow = 1)

```
As you can see, there appear to be some outliers on the high end. Most of the data lies between 10 and 20 percent, meaning that it is likely the client will have at least some options for improvement in this area

**RESEARCH QUESTION TWO**

## Can Cities Impact Healthy Behaviors?
As previously stated, I will primarily consider obesity as a result rather than a behavior. As a result, I've identified four healthy behaviors that a city can influence:
*"There is no leisure-time physical activity among persons over the age of 18" (LPA)
* "Sleeping fewer than 7 hours in adults over the age of 18" (SLEEP)
* "Binge drinking in adults over the age of 18" (BINGE)
* "Adults above the age of 18 who are currently smoking" (CSMOKING)

```{r}
summary(select(cities, "csmoking", "sleep", "lpa", "binge"))
```
```{r}
unhealthy_behavior <- summarize(cities, "csmoking" = max(csmoking)-min(csmoking), "sleep" = max(sleep)-min(sleep), 
                        "lpa" = max(lpa)-min(lpa), "binge" = max(binge)-min(binge))

unhealthy_behavior <- pivot_longer(unhealthy_behavior, everything(), names_to = "measure", values_to = "value")

plot_unhealthy <- ggplot(data = unhealthy_behavior) +
  geom_col(mapping = aes(x = reorder(measure, -value), y = value), fill = "red") +
  labs(title = "Difference Between Cities", x = "Unhealthy Behavior", y = "Size of Difference")
print(plot_unhealthy)
```
The disparity isn't as pronounced as it is in some of the poorest preventative services. The biggest disparity is in the lack of leisure-time physical exercise, which is 44.2 percent vs 12.60 percent. It's comparable, except the maximum and minimum values are significantly higher. It's odd, though, that different cities have such disparities in the percentages of people who engage in leisure-time physical activity.

I take a closer look at the variable that makes the most difference once more.

```{r}
plot_phy <- ggplot(data = cities) +
  geom_histogram(mapping = aes(x = lpa), na.rm = TRUE, binwidth = 2) + 
  labs(title = "Cities Without Leisurely Physical Activity", x = "Population Without Leisure Physical Activity", y = "Count of Cities")

box_phy <- ggplot(data = cities) +
  geom_boxplot(mapping = aes(y = lpa), na.rm = TRUE) + 
  labs(title = "Cities Without Leisurely Physical Activity", y = "Population Without Leisure Physical Activity")

ggarrange(plot_phy, box_phy,  ncol = 2, nrow = 1)
```
## Seeking Prevention

Now that we've established that cities use preventative services differently, we need to figure out why. What can the city do to encourage more people to use the services?

My initial hypothesis is based on the inclusion of access2, which is the percentage of the population that are uninsured. As the name implies this can tell us whether a population is not getting preventative care because they do not have insurance, making the services unaffordable. If this is the case, the small city could make a difference in the usage of preventative treatments by assisting their citizens in becoming insured or ensuring that the services are available in an accessible and affordable manner.
We've created a correlation matrix followed by a heatmap. We will  be looking at the use of preventative services. I'll be interested in any correlations with an absolute value above .65.
```{r}

correlated_use <- census%>%
  drop_na() %>%
  select(access2, dental, checkup, corem, corew, cholscreen, colon_screen, mammouse) %>%
  cor() 

print(correlated_use)

heatmap(correlated_use, main = "Correlations of Preventative Care", Colv = NA, Rowv = NA, margins = c(9, 9), scale = "none")

```
The relationships between access2 and dental, corem, corew, cholscreen, and colon screen are among the more intriguing. Also visible are connections between corem and corew, as well as correlations with dental, cholscreen, and colon screen. Surprisingly, dental has a link to cholscreen and colon screen.

It is surprising that there was no stronger link between access2 and checkup, or checkup and some of the other metrics.
However, access2 has the strongest connection with the most variables. This doesn't strictly confirm my notion (I'd need additional data), but it does give it some credence as a possibility.



**RESEARCH QUESTION 3**

## Does the use of health services make any Difference in the city?
The second consideration is whether or not using these services is beneficial. The client's purpose isn't to force residents to use its preventative services. Its goal is to improve the residents' health. Use of preventative services may be one of the areas where cities may make the most difference, but does their use have an impact on the city's health?
the following outcomes were used
"Stroke in people over the age of 18" (STROKE)
"Obesity in people beyond the age of 18" (OBESITY)
"All teeth are lost in adults over the age of 65." (TEETHLOST)
"Diabetes diagnosed in adults over the age of 18" (DIABETES)
"Cancer in adults over the age of 18 years (excluding skin cancer)" (CANCER)
"Chronic obstructive pulmonary disease (COPD) in people over the age of 18" (COPD)
"Coronary heart disease in adults above the age of 18" (CHD)
"Current asthma in people over the age of 18" (CASTHMA)
"Chronic renal disease in persons above the age of 18" (KIDNEY)
"Taking medication to treat high blood pressure in persons over the age of 18 who have high blood pressure" (BPMED)
"High cholesterol in persons over the age of 18 who have had a screening in the previous 5 years" (HIGHCHOL)

```{r}
summary(select(cities, "phlth", "mhlth", "bphigh", "arthritis", "stroke", "obesity", "teethlost", "diabetes", "cancer", "copd", "chd", 
               "casthma", "kidney", "bpmed", "highchol"))

```



```{r}
ggplot(data = census) + 
  geom_smooth(mapping = aes(x = access2, y = phlth), method = 'gam', color = 'purple', na.rm = TRUE) +
  geom_smooth(mapping = aes(x = access2, y = mhlth), method = 'gam', color = 'blue', na.rm = TRUE) + 
  labs(title = "Physical and Mental Health with Insurance", x = "Percent of Population Without Health Insurance", 
       y = "Percent of Population With Poor Physical Health Over 14 Days") +
  annotate("text",x = 39, y = 21, label = "Poor Physical Health Over 14 Days", color = 'purple') + 
  annotate("text",x = 44, y = 15, label = "Poor Mental Health Over 14 Days", color = 'blue')
```
As you can see, the number of people who have battled with physical health and mental health increases in cities as the number of people without health insurance rises. This is a fascinating result, especially since we've already seen that health insurance corresponds with the usage of other measurable preventative treatments. There may also be preventative services and treatments that were not measured but are nonetheless influenced by health insurance.

We can look at the function of health insurance in high cholesterol and cholesterol testing as another, particularly intriguing example:
```{r}
par(mfrow=c(2,2))
scatter_insure <- ggplot(data = census) + 
  geom_point(mapping = aes(x = cholscreen, y = highchol, color = access2), na.rm = TRUE) +
  labs(title = "The Impact of High Cholesterol on Cholesterol Screenings", x = "Cholesterol Screenings", 
       y = "Percent Population with High Cholesterol")

line_insure <- ggplot(data = census) + 
  geom_smooth(mapping = aes(x = access2, y = cholscreen), color = 'purple', na.rm = TRUE) +
  geom_smooth(mapping = aes(x = access2, y = highchol), color = 'blue', na.rm = TRUE)+
  labs(title = "The Impact of Insurance on High Cholesterol and Screenings", 
       x = "Percent of Population Without Health Insurance", y = "Percent with High Cholesterol or Screened") +
  annotate("text",x = 17, y = 80, label = "Cholesterol Screenings", color = 'purple') + 
  annotate("text",x = 50, y = 37, label = "High Cholesterol", color = 'blue')

ggarrange(scatter_insure, line_insure, nrow = 1, ncol = 2)
```
As you can see, the greater the number of people who have high cholesterol, the more people who are screened for it. When health insurance is included in, however, we can see that people without health insurance are more likely to have high cholesterol and are less likely to be evaluated for it.

Let's have a look at the overall correlations:


```{r}

correlated_prevention <- census%>%
  drop_na() %>%
  select(access2, checkup, corem, corew, cholscreen, colon_screen, mammouse, 
         dental, phlth, mhlth, stroke, highchol, bphigh, bpmed, obesity, copd,
         diabetes, cancer, kidney, arthritis, chd, teethlost, casthma) %>%
  cor() 


print(correlated_prevention)

heatmap(correlated_prevention, main = "Prevention and Outcomes", Colv = NA, Rowv = NA, margins = c(10, 10), scale = "none")

```
Observations:

Access2 has a link to phlth, mhlth, and teethlost, which was previously discovered to have a link to the utilization of preventative treatments.
There is a link between checkup and bphigh and bpmed.
Corem and corew have links to phlth, mhlth, and tooth loss.
Only Corew is compatible with diabetes and kidney disease.
Cholscreen has an odd relationship with cancer and health.
phlth, mhlth, and teethlost are used in colon screen.
Dental problems include phlth, mhlth, stroke, obesity, copd, diabetes, kidney failure, and tooth loss.
There's always the chance of coincidental correlations, and everything is exacerbated by the fact that many of these outcomes are highly correlated. High levels of diabetes, coronary heart disease, and COPD, for example, are all linked to an increased risk of stroke:


##Key Findings
* Because a population's health insurance, usage of preventative services, and even harmful behaviors can differ throughout places, there is a chance (but not a guarantee) that they will be influenced by them.
* It does not appear that the size of the city makes a difference.
* Negative health outcomes are linked to a high prevalence of unhealthy habits and/or insufficient utilization of preventative interventions.
* As a result, the research does not rule out the possibility that a city can reduce the number of strokes, coronary heart disease, high cholesterol, diabetes, and other adverse health consequences.
* The two variables that differ the most between cities are also the ones that correlate the most with a range of other variables.
* Failure to employ many preventative services is linked to a lack of health insurance.
* This lends some credence to the theory that a part of the population is deterred from using these services due to their high cost.
* Physical inactivity during leisure time is linked to a variety of unfavorable health effects.


## Limitations
This analysis has a number of flaws, the most notable of which is the lack of data pertaining to the envisioned customer city. I recommend that any small city look into the health issues that are now plaguing its population for additional research and more precise, accurate recommendations. The CDC's data can be used to create a model for future research. Interventions can thus be tailored to the specific health issues that a group faces.
Missing values has an impact on the reliability of the results of the analysis. 



